Naming Anonymous JavaScript Functions

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
table 6 was updated.

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{ | l | l | l |}
  \hline
   Description &Pattern &  Name \\ 
  \hline 
   Primitive & value & value.toString() \\ 
  \hline 
   Variable & id & id \\ 
  \hline 
   GetProp & e.id & Name(e).id \\ 
  \hline 
   GetElem & e1[e2] & Name(e1)+``['+'Name(e2)+``]'' \\ 
  \hline 
   Add & e1 op e2 & Name(e1)+op+Name(e2) \\ 
  \hline 
   Condition & cond?e1:e2 & Name(e1)+":"+Name(e2) \\ 
  \hline 
  \end{tabular}
  }
\caption{JavaScript Expression Reduction to a Name. Expressions which match an entry in the pattern column are converted as shown in the Name column. Here \texttt{e} indicates an expression, \texttt{id} indicates an identifier, \texttt{+} means string concatenation and \texttt{Name()} means we apply the pattern matching recursively.}
\label{expression-reduction} 
\end{table}

@@

\begin{table*}[tb]
\centering
\begin{tabular}{|l|l|}
\hline
Example Code & Static Function-Object Consumption Name \\
\hline
Sec.~\ref{sec:arrayLiteral} & YUI.add[event-focus]()/\_attach/Event.\_attach() \\
\hline
Sec.~\ref{sec:propid} & eventPool\_createObject \\
\hline
Fig.~\ref{fig:jQueryEach} outer & jQuery.each(ajaxStart) \\
\hline
Fig.~\ref{fig:jQueryEach} inner & jQuery.fn[o] \\
\hline
Sec.~\ref{sec:propexpressions}  & define/viewport[get+D] \\
\hline
Fig.~\ref{fig:classnamemanager} outer & YUI.add[classnamemanager]()/Y.ClassNameManage\verb|<| \\
\hline
Fig.~\ref{fig:classnamemanager} inner & YUI.add[classnamemanager]()/Y.ClassNameManager/getClassName \\
\hline
Sec.~\ref{sec:funcprop} inner & ?????????????\\
\hline
Fig.~\ref{fig:registerWin} inner & registerWin\verb|<| \\
\end{tabular}
\label{table:examples}
\caption{Results from applying the approach in Sec.~\ref{sec:foc} to the examples in the paper at the point given in the first column.
Full names are listed, even in cases where our example code omitted the enclosing function scope.}
\end{table*}

>>>>

\begin{table}
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l |}
  \hline
   Description &Pattern &  Name \\ 
  \hline 
   Primitive & value & value.toString() \\ 
  \hline 
   Variable & id & id \\ 
  \hline 
   GetProp & e.id & Name(e).id \\ 
  \hline 
   GetElem & e1[e2] & Name(e1)+``['+'Name(e2)+``]'' \\ 
  \hline 
   Add & e1 op e2 & Name(e1)+op+Name(e2) \\ 
  \hline 
   Condition & cond?e1:e2 & Name(e1)+":"+Name(e2) \\ 
  \hline 
  \end{tabular}
  }
\caption{JavaScript Expression Reduction to a Name. Expressions which match an entry in the pattern column are converted as shown in the Name column. Here \texttt{e} indicates an expression, \texttt{id} indicates an identifier, \texttt{+} means string concatenation and \texttt{Name()} means we apply the pattern matching recursively.}
\label{expression-reduction} 
\end{table}

@@

\begin{table*}[tb]
\centering
\scalebox{1}{
\begin{tabular}{|l|l|}
\hline
Example Code & Static Function-Object Consumption Name \\
\hline
Sec.~\ref{sec:arrayLiteral} outer & YUI.add(event-focus)/\_attach \\
\hline
Sec.~\ref{sec:arrayLiteral} inner & YUI.add(event-focus)/\_attach/Event.\_attach() \\
\hline
Sec.~\ref{sec:propid} & eventPool.\_createObject \\
\hline
Fig.~\ref{fig:jQueryEach} outer & jQuery.each(ajaxStart) \\
\hline
Fig.~\ref{fig:jQueryEach} inner & jQuery.fn[o] \\
\hline
Sec.~\ref{sec:propexpressions}  & define/viewport[get+D] \\
\hline
Fig.~\ref{fig:classnamemanager} outer & YUI.add(classnamemanager)/Y.ClassNameManager\textless \\
\hline
Fig.~\ref{fig:classnamemanager} inner & YUI.add(classnamemanager)/Y.ClassNameManager/getClassName \\
\hline
Sec.~\ref{sec:funcprop} inner & setVisible/cb\textless\\
\hline
Fig.~\ref{fig:registerWin} inner & registerWin/ \\
\hline
\end{tabular}
}
\label{table:examples}
\caption{Results from applying the approach in Sec.~\ref{sec:foc} to the examples in the paper at the point given in the first column.
Full names are listed, even in cases where our example code omitted the enclosing function scope.}
\end{table*}
